**Operating model**

### 2023-03-06 Rmd/mseMac.Rmd
with same code

#plot(prj,probs=0,worm=seq(4))+facet_grid(qname~stock,scale="free")

ggplot()+
  geom_line( aes(ssb,catch,col=.id),   data=eqCurves)+
  geom_point(aes(ssb,catch,col=.id),data=subset(ts,year==2040))
```

>>>>

#plot(prj,probs=0,worm=seq(4))+facet_grid(qname~stock,scale="free")
```

```{r, check, fig.height=6,fig.width=8}
ggplot()+
  geom_line( aes(ssb,catch,col=.id),   data=eqCurves)+
  geom_point(aes(ssb,catch,col=.id),data=subset(ts,year==2040))+
  theme_bw()+theme(legend.position="bottom")+
  xlab("SSB")+ylab("Yield")
```

### 2023-03-06 Rmd/omMac.Rmd
with same code

```{r echo=FALSE, warning=FALSE, cache=FALSE, eval=TRUE}
load(file.path(dropboxdir,"data/inputs/ices.RData"))
ices=ices[["mac.27.nea"]]
ices=window(ices,start=1991)

>>>>

```{r echo=FALSE, warning=FALSE, cache=FALSE, eval=TRUE}
library(FLCore)
library(FLBRP)
library(FLasher)

load(file.path(dropboxdir,"data/inputs/ices.RData"))
ices=ices[["mac.27.nea"]]
#ices=window(ices,start=1991)
